\documentclass[margin,line]{res}
\usepackage[dvipsnames,table,xcdraw]{xcolor}
\usepackage{mdframed}
% \usepackage{txfonts}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 
\raggedbottom

\usepackage{xcolor}
\definecolor{linkblue}{HTML}{0000EE}
\usepackage[colorlinks=true, linkcolor=linkblue, urlcolor=linkblue, citecolor=linkblue]{hyperref}

\usepackage{bm}
\usepackage[symbol]{footmisc}

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}
 


\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 

\begin{document}

% \vspace{-.35cm}
\name{Joseph R. Farah \vspace*{.1in}}
\begin{resume}


\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}
Las Cumbres Observatory and Global Telescope & \textit{ORCID}: \href{https://orcid.org/0000-0003-4914-5625}{0000-0003-4914-5625} \\             
6740 Cortona Dr  & {\it E-mail:} \href{mailto:jfarah@lco.global}{\color{blue}jfarah@lco.global}\\
Goleta, CA 93117  & {\it Website:} \href{http://jrfarah.com}{\color{blue}http://jrfarah.com} \\
USA & \textit{Citations}: \href{https://scholar.google.com/citations?hl=en&user=EVnW70sAAAAJ}{\color{blue}Google Scholar profile}\\
\end{tabular}

%\section{\sc Objective}
%Seeking a summer internship in {\bf computer vision} in either application or research

\section{\sc Research Interests}

Astrophysics, supernovae, photon ring, radio astronomy, black holes, magnetars, very long baseline interferometry, space VLBI, strong gravity, Bayesian modeling, magnetohydrodynamics, frameworks, machine learning, deep learning
%probabilistic graphical models,


\vspace*{-1mm}
\section{\sc Education}
\label{sec:education}

{\bf University of California Santa Barbara}, Santa Barbara, CA, USA\hfill 2021--2026

\vspace{-.35cm}
{\em Ph.D. in Physics (in progress)}\\
{\em M.A. in Physics (completed) } \hfill 2023

{\bf University of Massachusetts Boston}, Boston, MA, USA\hfill 2017--2021

\vspace{-.35cm}
{\em B.S. in Physics, summa cum laude, with distinction}


% \textit{GPA}: 3.9/4.0 
% \textit{GPA (physics)}: 3.909/4.0
\vspace{-.6cm}

\section{\sc {\color{Maroon} Selected\\ Honors} and Awards} 
\vspace*{0.67cm}

% \vspace*{-2mm}
UC Santa Barbara Mananya Tantiwiwat Award \hfill 2025

\vspace*{-2mm}
Broida-Hirschfelder Fellowship  \hfill 2025  \\
{\color{gray}\textsc{citation}: \textit{In recognition of his project uncovering the secrets of the strangest object in the universe, the black hole photon ring.}}

\vspace*{-2mm}
$1^\textrm{st}$ Place Award, UC Santa Barbara Grad Slam  \hfill 2025 \\
{\color{gray}\textit{Round 1 (Physics and Chemistry)}}

\vspace*{-2mm}
UC Santa Barbara GSA Excellence in Teaching Award (nominated) \hfill 2025 

\vspace*{-2mm}
UC Santa Barbara Academic Senate Outstanding Teaching Assistant Award (nominated) \hfill 2024 

\vspace*{-2mm}
Event Horizon Telescope {Early Career Award} \hfill 2022 \\
{\color{gray}\href{https://twitter.com/ehtelescope/status/1602826998346551296}{\textsc{citation}}: \textit{For his leadership and contribution to the dynamic imaging of the interferometric data used to image Sgr A*.}}

\vspace*{-2mm}
{\color{Maroon}LeRoy Apker Award  \hfill 2021}\\
{\color{gray}\href{https://www.aps.org/funding-recognition/award/leroy-apker-award}{\textsc{citation}}: \textit{For the invention of the selective dynamical imaging method, with applications for studying rapidly-varying black holes.}}

\vspace*{-2mm}
UC Santa Barbara James and Mary Jo Hartle Graduate Fellowship  \hfill 2021

\vspace*{-2mm}
{\color{Maroon}National Science Foundation Graduate Research Fellowship  \hfill 2021--2026}

\vspace*{-2mm}
Arthur W. Martin III Scholarship \hfill 2021


\vspace*{-2mm}
{LeRoy Apker Award (finalist) (2 times)  \hfill 2020, 2021}

\vspace*{-2mm}
{\color{Maroon} Breakthrough Prize in Fundamental Physics (co-recipient) \hfill 2020}

\vspace*{-2mm}
Northrop Grumman Scholarship \hfill 2020


\vspace*{-2mm}
{\color{Maroon} Barry M. Goldwater Scholarship \hfill 2019}



\vspace*{-2mm}
National Science Foundation Diamond Achievement Award$^\ddag$ \hfill 2019



\vspace*{-2mm}
Named one of Boston's \textrm{\color{blue}{\href{https://www.bizjournals.com/boston/news/2019/12/12/25-under-25-here-are-young-achievers-in-the-boston.html}{25 Under 25}}} \hfill 2019
\newpage

\vspace*{-2mm}
Alton J. Brann Endowed Scholarship \hfill 2019

\vspace*{-2mm}
Smithsonian Fellowship \hfill 2018, 2019

\vspace*{-2mm}
Oracle Fellowship \hfill 2018, 2019

\vspace*{-2mm}
AJAS/AAAS Lifetime Fellowship \hfill 2018

\vspace*{-2mm}
Chancellor's Scholarship, University of Massachusetts Boston \hfill 2017--2021

\vspace*{-2mm}
$2^\textrm{nd}$ Place Award, Massachusetts State Science and Engineering Fair \hfill 2017

\vspace*{-2mm}
$1^\textrm{st}$ Place Award, Massachusetts State Science and Engineering Fair \hfill 2016


\vspace{+.4cm}
\section{\sc Selected Work and Research Experience}
{\bf Las Cumbres Observatory}\hfill 2021 - Present


\vspace{-.4cm}
{\em NSF Graduate Research Fellowship --- Goleta, CA}

\begin{changemargin}{-0.0cm}{2.5cm} 
I use the LCO global network of telescopes to perform optical and spectroscopic follow-up of a wide variety of supernovae and transients. Using rapid follow-up observations combined with new shock cooling physics, I seek to better characterize and understand the mass stripping mechanism of Type IIb supernovae, and the underlying mechanisms powering superluminous supernovae. Additionally, I help with infrastructure maintenance and development for the robotic LCO platform.

\textit{Supervisor: Andy Howell}
\end{changemargin}



{\bf Harvard-Smithsonian Center for Astrophysics}

\vspace{-.4cm}
{\em Member of the Black Hole Explorer Collaboration --- Cambridge, MA} \hfill 2020 - Present

\begin{changemargin}{-0.0cm}{2.5cm} 
I develop analytic and deep learning techniques for measuring physical properties from the black hole's photon ring. Along with the BHEX collaboration, I assist in the preparation and development of the BHEX spacecraft, an orbiting radio telescope which will interface with the EHT and use space VLBI to make high resolution images and movies of black holes.

\textit{Supervisor: Alex Lupsasca}
\end{changemargin}


% \vspace{-.4cm}
{\em Smithsonian Fellowship with the Event Horizon Telescope --- Cambridge, MA} \hfill 2018 - 2021

\begin{changemargin}{-0.0cm}{2.5cm} 
I image supermassive black holes and assist in observations using the Event Horizon Telescope in order to help take the first ever pictures of black holes. I explored alternative parametric representations of shadows in the Kerr metric and non-standard GR theories, and methods constraining the angular momentum of rotating black holes in EHT data using image- and Fourier-domain feature extraction methods. As an undergraduate, I was the first and only junior collaborator of the EHT Consortium. 

\textit{Supervisor: Michael Johnson}
\end{changemargin}

{\bf Quantum Computing Research Group}\hfill 2019 - 2021

\vspace{-.4cm}
{\em Research Intern with Dr. Alioscia Hamma  --- Boston, MA}

\vspace{.1cm}
{\bf Harvard Laboratory for Particle Physics and Cosmology}\hfill 2017 - 2018

\vspace{-.4cm}
{\em Research Intern with Dr. Melissa Franklin --- Cambridge, MA}

% 
{\bf QBism Research Group}\hfill 2017 - 2019

\vspace{-.4cm}
{\em Research Intern with Dr. Christopher Fuchs  --- Boston, MA}

{\bf Harvard School for Engineering and Applied Sciences}\hfill Summer 2016

\vspace{-.4cm}
{\em Summer Research Intern mentored by Dr. Chinwendu Enyioha --- Cambridge, MA}

{\bf Tufts Department of Astrophysics}\hfill Summer 2015

\vspace{-.4cm}
{\em Summer Research Intern mentored by Dr. Anna Sajina --- Medford, MA}






\vspace{+.4cm}
\section{\sc Students mentored}

\textbf{Undergraduate}
\begin{itemize}
    \item[] Courtney Duong (UC Santa Barbara) \hfill 2024 - Present
    \begin{itemize}
        \item[] Project: Convolutional neural network for extraction of the $n=1$ black hole photon ring
        \item[] Award: \textit{Gene and Susan Lucas Undergraduate Research Scholarship}
        \item[] Award: \textit{Edison STEM Research Scholarship}
    \end{itemize}
    \item[] Franklin Myhre (UC Santa Barbara) \hfill 2024 - Present
    \begin{itemize}
        \item[] Project: Development of a \texttt{python} library for automated image-domain subring extraction
    \end{itemize}
    \item[] Sanjit Masanam (UC Santa Barbara) \hfill 2024 - Present
    \begin{itemize}
        \item[] Award: \textit{2025 Goldwater Scholarship (nominated)}
        \item[] Award: \textit{2025 Ernest F. Hollings Scholarship}
    \end{itemize}
    \item[] Songgun Lee (UC Santa Barbara) \hfill 2024 - Present
    \begin{itemize}
        \item[] \textit{Co-founder at Masterminding}
    \end{itemize}
    \item[] Tazzy Imbabi (UC Santa Barbara) \hfill 2024
    \begin{itemize}
        \item[] Project: Exploration of selective dynamical imaging applications to BHEX
    \end{itemize}
\end{itemize}


% \section{\sc Academic\\ Service}
\vspace{+.4cm}
\section{\sc Invited Talks, Panels, Interviews and Filmography}

The first 4 years of SN 1993J revisited. UC Berkeley, Berkeley, CA. Invited seminar speaker. September 2025. 

Lense-Thirring precessing magnetar engine drives a superluminous supernova. UC Berkeley, Berkeley, CA. Invited speaker for Multi-RAPTOR colloquium. September 2025. 

Extragalactic science with the Vera C. Rubin Observatory. Santa Barbara Museum of Natural History. Invited speaker for public lecture. August 2025. {\color{blue}\href{https://www.sbnature.org/visit/calendar/8760/new-frontiers-in-astronomy-powered-by-the-rubin-observatory}{Event URL.}}

Probing fundamental physics using high-energy astrophysical phenomena. Goleta, CA. Invited speaker for the Las Cumbres Observatory Science Advisory Committee. August 2025.

Machine- and deep-learning-driven angular momentum inference from Black Hole Explorer observations of the n=1 photon subring. \textit{Topics in Gravitational Physics}. Presentation at the APS Global Physics Summit. March 2025. {\color{blue}\href{https://summit.aps.org/events/APR-C20/8}{Event URL.}}

Current and Future Impacts of Survey Capabilities on the Stripped Envelope Problem. Kavli Institute for Theoretical Physics, Santa Barbara, CA. February 2025. 

Shock-cooling Constraints via Early-time Observations of the Type IIb SN 2022hnt. Kavli Institute for Theoretical Physics, Santa Barbara. February 2025. 

The Black Hole Explorer and the Edge of the Universe. Santa Barbara Museum of Natural History. April 2025. Invited speaker for public lecture. {\color{blue}\href{https://www.sbnature.org/visit/calendar/8642/the-black-hole-explorer-and-the-edge-of-the-universe}{Event URL.}}

The Black Hole Explorer. Santa Barbara, CA. Invited speaker for \textit{Astronomy on Tap}. December 2024. {\color{blue}\href{https://lco.global/aot/december-5-2024/}{Event URL.}}

What does an astronomer do? Canalino Elementary School. October 2024. Invited educational outreach speaker. 

Inferring black hole spin from images of the photon ring. Vanderbilt University VandyGRAF initiative. September 2024. Invited speaker. 

The Biggest Telescopes! Aliso Elementary School. October 2023. Invited educational outreach speaker. 

Imaging the Black Hole at Our Galaxy's Center. Santa Barbara Museum of Natural History. May 2023. Invited speaker for public lecture. {\color{blue}\href{https://www.sbnature.org/visit/calendar/7329/free-public-astronomy-talk-imaging-the-black-hole-at-our-galaxys-center}{Event URL.}}

LCO's Top 9 Tips For Taking Your Best Black Hole Photo. Medford High School, Medford, Massachusetts. Invited speaker for honors and AP physics classes. 2022.

LCO's Top 9 Tips For Taking Your Best Black Hole Photo. Santa Barbara, CA. Invited speaker for \textit{Astronomy on Tap}. November 2022. {\color{blue}\href{https://astronomyontap.org/event/astronomy-on-tap-santa-barbara-2/}{Event URL.}}

Selective Dynamical Imaging of Interferometric Data and the Second Image of a Black Hole. University of California, Santa Barbara, California. Invited speaker for \textit{Astro Tea}. June 2022.

New EHT Image of Sagittarius A*. \textit{Montecito Journal}. June 2022. {\color{blue}\href{https://www.montecitojournal.net/2022/06/07/new-eht-image-of-sagittarius-a/}{Article URL.}}

Santa Barbara Astronomer Bags a Black Hole.
\textit{Santa Barbara Independent}. June 2022. {\color{blue}\href{https://www.independent.com/2022/05/19/santa-barbara-astronomer-bags-a-black-hole/}{Article URL.}}

Research in Review, 2022.
\textit{The Daily Nexus}. May 2022. {\color{blue}\href{https://dailynexus.com/2022-05-26/research-in-review/}{Article URL.}}

Spotted! Astrophysicists Release the First Ever Image of a Black Hole in the Milky Way.
\textit{The Bottom Line}. May 2022. {\color{blue}\href{https://thebottomline.as.ucsb.edu/2022/06/spotted-astrophysicists-release-the-first-ever-image-of-a-black-hole-in-the-milky-way}{Article URL.}}


Joseph Farah '21 Among Researchers to Capture First Image of Black Hole.
\textit{UMB News}. May 2022. {\color{blue}\href{https://www.umb.edu/news/detail/joseph_farah_21_among_researchers_to_capture_first_image_of_black_hole}{Article URL.}}

South Coast scientist played a critical role in capturing the first image of our galaxy's black hole. \textit{NPR via KCLU}. May 2022. {\color{blue}\href{https://www.kclu.org/local-news/2022-05-12/south-coast-scientist-played-a-critical-role-in-capturing-the-first-image-of-our-galaxys-black-hole}{Article URL.}}

AskScience AMA Series: We're Event Horizon Telescope scientists with groundbreaking results on our own galaxy; Ask Us Anything. \textit{Reddit}. May 2022. {\color{blue}\href{https://old.reddit.com/r/askscience/comments/unyg77/askscience_ama_series_were_event_horizon/}{Article URL.}}

Sagittarius A* Revealed. \textit{ScienceX}. May 2022. {\color{blue}\href{https://sciencex.com/wire-news/413826795/sagittarius-a-revealed.html}{Article URL.}}

Astronomers reveal first image of the black hole at the heart of our galaxy. Sandy Seale, \textit{Las Cumbres Observatory}. May 2022. {\color{blue}\href{https://lco.global/news/astronomers-reveal-first-image-of-the-black-hole-at-the-heart-of-our-galaxy/}{Article URL.}}


Sagittarius A* Revealed. Sonia Fernandez \& Sandy Seale, \textit{UC Santa Barbara News}. May 2022. {\color{blue}\href{https://www.news.ucsb.edu/2022/020632/astronomers-reveal-first-image-black-hole-heart-our-galaxy}{Article URL.}}


Meet the 2021 LeRoy Apker Award Recipients. David Barnstone, \textit{American Physical Society}. February 2022. {\color{blue}\href{https://www.aps.org/publications/apsnews/202202/apker.cfm}{Article URL.}}

Looking Deep into Space: Grad student and 2021 LeRoy Apker Award winner Joseph Farah brings his curiosity and drive to Las Cumbres Observatory. David Barnstone, \textit{The Current}. February 2022. {\color{blue}\href{https://www.news.ucsb.edu/2022/020559/looking-deep-space}{Article URL.}}

What Lies Within: Imaging the Galactic Center. April 2022. April APS Meeting, New York City, New York. Invited speaker for American Physical Society.

Rising EHT Scientist Awarded Prestigious Physics Award. Nadia Whitehead, \textit{Center for Astrophysics $\vert$ Harvard-Smithsonian}. October 2021. {\color{blue}\href{https://www.cfa.harvard.edu/news/rising-eht-scientist-awarded-prestigious-physics-award}{Article URL.}}

UMass Boston Alum Wins Prestigious National Academic Award in Physics. Danielle Bilotta, \textit{UMB News}. November 2021. {\color{blue}\href{https://www.umb.edu/news/detail/umass_boston_alum_wins_prestigious_national_academic_award_in_physics}{Article URL.}}

The First Image of a Black Hole. Seagrave Memorial Observatory, North Scituate, Rhode Island. Invited speaker for Skyscrapers, Inc. 2021.

Galison, P. L. (Director). 2021. \textit{Black Holes: The Edge of All We Know.} Film. Sandbox Films. \href{https://www.netflix.com/title/81343342}{View on Netflix.}

Very Long Baseline Interferometry and the Event Horizon Telescope. University of Massachusetts, Boston, Massachusetts. Invited speaker for Astronomy 121. 2019 (2 times), 2020 (2 times).

Physics Student Named Finalist for Prestigious National Academic Award. DeWayne Lehman, \textit{UMass Boston News}. July 2020. {\color{blue}\href{https://www.umb.edu/news/detail/physics_student_named_finalist_for_prestigious_national_academic_award}{Article URL.}}

Drag Racing and Black Hole Physics. Catherine Steffel, \textit{Symmetry Magazine}. January 2020. {\color{blue}\href{https://www.symmetrymagazine.org/article/drag-racing-and-black-hole-physics}{Article URL.}}

Fortnite flashback: Just how accurate was the black hole that launched Chapter 2? Doris Elin Urrutia, \textit{Space.com}. February 2020. {\color{blue}\href{https://www.atlasobscura.com/articles/biggest-telescope-black-hole}{Article URL.}}

Galison, P. L. (Director). 2019. \textit{Portrait of a Shadow.} Film. Sandbox Films.


UMass Boston Physics Major Shares in \$3M Breakthrough Prize for Black Hole Image. Colleen Locke, \textit{UMass Boston News}. September 2019. {\color{blue}\href{https://www.umb.edu/news/detail/umass_boston_physics_major_shares_in_3m_breakthrough_prize_for_black_hole_image}{Article URL.}}

Student Spotlight: Joseph Farah. Lisa Allen, \textit{UMass Boston News}. September 2019. {\color{blue}\href{https://www.umb.edu/news/detail/student_spotlight_joseph_farah}{Article URL.}}

Seeing the Unseeable: The First Image of a Black Hole. University of Massachusetts Boston, Boston, Massachusetts. May 2019.

Scientists Needed to Build a ‘Planet-Sized Telescope’ to See the Black Hole. Jessica Heister, \textit{Atlas Obscura}. April 2019. {\color{blue}\href{https://www.space.com/fortnite-chapter-2-black-hole-science.html}{Article URL.}}

Two UMass Boston Students Earn Prestigious Goldwater Scholarships. Maedot Kassa, \textit{UMass Boston News}. April 2019. {\color{blue}\href{https://www.umb.edu/news/detail/two_umass_boston_students_earn_prestigious_goldwater_scholarships}{Article URL.}}


Imaging a Black Hole with the Event Horizon Telescope. Harvard University, Cambridge, MA. April
2019.


\newpage
\vspace{+.4cm}
\section{{\sc Publications (first-author)  \\ \vspace{0.3cm} {\footnotesize \textbf{\color{Maroon} Stats (all papers)}: \\Citations: 19,100+ \\ \vspace{0.1cm} \noindent Ref'd Papers: 118+ \vspace{0.1cm} \\ $h$-index: 37 \\ i10-index: 73}} \\ }

% \textbf{NB:} Please see full list of publications on page 6

8. \textbf{J. R. Farah}, Lupsasca, A., Quataert, E., Johnson, M. D. 2025. \textit{Interferometric inference of black hole spin from photon ring size and brightness}. Submitted to ApJ. \href{https://arxiv.org/abs/2509.23628}{arXiv:2509.23628}.

7. \textbf{J. R. Farah}, Prust, L. J., Howell, D. A., \textit{et al.}. 2025. \textit{Lense-Thirring precessing magnetar engine drives a superluminous supernova}. Submitted to \textit{Nature}, positive referee report received, response submitted. \href{https://arxiv.org/abs/2509.08051}{arXiv:2509.08051}.

6. \textbf{J. R. Farah}, Howell, D. A., Hiramatsu, D., \textit{et al.}. 2025. \textit{When IIb Ceases To Be: Bridging the Gap Between IIb and Short-plateau Supernovae}. Submitted to ApJ, positive referee report received. \href{https://arxiv.org/abs/2509.12470}{arXiv:2509.12470}.

5. \textbf{J. R. Farah}, Prust, L. J., Terreran, G., \textit{et al.}. 2025. \textit{The First 4 Years of SN 1993J Revisited: Geometric $m$-ring Modeling of the Radio Shell with Closure Quantities Only}. arXiv e-prints, \href{https://arxiv.org/abs/2509.20601}{arXiv:2509.20601}.

4. \textbf{J. R. Farah}, Davelaar, J., Palumbo, D., Johnson, M., Delgado, J. 2025. \textit{Machine and Deep Learning-driven Angular Momentum Inference from BHEX Observations of the n = 1 Photon Ring}. \apj, 983, \href{https://iopscience.iop.org/article/10.3847/1538-4357/adbbe3}{185}. \href{https://arxiv.org/abs/2411.01060}{arXiv:2411.01060}.

3. \textbf{J. R. Farah}, Howell, D. A., Terreran, G., \textit{et al.}. 2025. \textit{Shock-cooling Constraints via Early-time Observations of the Type IIb SN 2022hnt}. \apj, 984, \href{https://iopscience.iop.org/article/10.3847/1538-4357/adad5a}{60}. \href{https://arxiv.org/abs/2501.17221}{arXiv:2501.17221}.


2. \footnote[$^S$]{\noindent $^S$This was the seventh paper of the 10-paper first Galactic Center results series from the Event Horizon Telescope, presenting the second image of a black hole and the first horizon-scale images of Sgr A$^\ast$.}\textbf{J. R. Farah}, Galison, P., Akiyama, K., \textit{et al.}. 2022. \textit{Selective Dynamical Imaging of Interferometric Data}. \apjl, 930, \href{https://iopscience.iop.org/article/10.3847/2041-8213/ac6615}{L18}. \href{https://arxiv.org/abs/2409.08321}{arXiv:2409.08321}.

1. \textbf{J. R. Farah}, Pesce, D. W., Johnson, M. D., Blackburn, L. 2020. \textit{On the Approximation of the Black Hole Shadow with a Simple Polar Curve}. \apj, 900, \href{https://iopscience.iop.org/article/10.3847/1538-4357/aba59a}{77}. \href{https://arxiv.org/abs/2007.06732}{arXiv:2007.06732}.




\vspace{+.4cm}
\section{\sc Publications (\fcolorbox{red}{white}{Major} or normal contribution)} 
\label{sec:publications}

(last updated: Sep 2025)

110. Wang, Z. Y., Pastorello, A., Cai, Y. Z., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Massive stars exploding in a He-rich circumstellar medium: XI. Diverse evolution of five Ibn SNe 2020nxt, 2020taz, 2021bbv, 2023utc, and 2024aej}. \aap, 700, A156. \href{https://arxiv.org/abs/2506.15139}{arXiv:2506.15139}.

109. Bostroem, K. A., Valenti, S., Sand, D. J., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Late-time Hubble Space Telescope Ultraviolet Spectra of SN 2023ixf and SN 2024ggi Show Ongoing Interaction with Circumstellar Material}. arXiv e-prints, \href{https://arxiv.org/abs/2508.11756}{arXiv:2508.11756}.

108. Kwok, L. A., Singh, M., Jha, S. W., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{JWST and Ground-based Observations of the Type Iax Supernovae SN 2024pxl and SN 2024vjm: Evidence for Weak Deflagration Explosions}. \apjl, 989, L33. \href{https://arxiv.org/abs/2505.02944}{arXiv:2505.02944}.

107. Gagliano, A., Villar, V., Matsumoto, T., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Evidence for an Instability-induced Binary Merger in the Double-peaked, Helium-rich Type IIn Supernova 2023zkd}. \apj, 989, 182. \href{https://arxiv.org/abs/2502.19469}{arXiv:2502.19469}.

106. \'Sniegowska, M., Trakhtenbrot, B., Makrygianni, L., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{AT 2019aalc: A Bowen Fluorescence Flare with a Precursor Flare in an Active Galactic Nucleus}. \apj, 989, 173. \href{https://arxiv.org/abs/2505.00083}{arXiv:2505.00083}.

105. Makrygianni, L., Arcavi, I., Newsome, M., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{The Double Tidal Disruption Event AT 2022dbl Implies that at Least Some ``Standard'' Optical Tidal Disruption Events Are Partial Disruptions}. \apjl, 987, L20. \href{https://arxiv.org/abs/2505.16867}{arXiv:2505.16867}.

104. Dahale, R., Cho, I., Moriyama, K., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Origin of the ring ellipticity in the black hole images of M87$^{*}$}. \aap, 699, A279. \href{https://arxiv.org/abs/2505.10333}{arXiv:2505.10333}.

103. Park, S. H., Rho, J., Yoon, S. C., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Near-Infrared Spectroscopy and Detection of Carbon Monoxide in the Type II Supernova SN 2023ixf}. arXiv e-prints, \href{https://arxiv.org/abs/2507.11877}{arXiv:2507.11877}.

102. Goddi, C., Carlos, D. F., Crew, G. B., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{First polarization study of the M87 jet and active galactic nuclei at submillimeter wavelengths with ALMA}. \aap, 699, A265. \href{https://arxiv.org/abs/2505.10181}{arXiv:2505.10181}.

101. Jiang, S. Q., Xu, D., van Hoof, A. P., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{EP240801a/XRF 240801B: An X-Ray Flash Detected by the Einstein Probe and the Implications of Its Multiband Afterglow}. \apjl, 988, L34. \href{https://arxiv.org/abs/2503.04306}{arXiv:2503.04306}.

100. Sun, H., Li, W. X., Liu, L. D., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{A fast X-ray transient from a weak relativistic jet associated with a type Ic-BL supernova}. Nature Astronomy, 9, 1073-1085. \href{https://arxiv.org/abs/2410.02315}{arXiv:2410.02315}.

99. Kumar, H., Berger, E., Blanchard, P. K., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{A Near-infrared Search for Helium in the Superluminous Supernova SN 2024ahr}. \apj, 987, 127. \href{https://arxiv.org/abs/2501.01485}{arXiv:2501.01485}.

98. Singh, M., Kwok, L. A., Jha, S. W., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Photometry and Spectroscopy of SN 2024pxl: A Luminosity Link Among Type Iax Supernovae}. arXiv e-prints, \href{https://arxiv.org/abs/2505.02943}{arXiv:2505.02943}.

97. Jacobson-Gal\'an, W., Dessart, L., Davis, K., \textit{et al.}. 2025. \textit{Final Moments III: Explosion Properties and Progenitor Constraints of CSM-Interacting Type II Supernovae}. arXiv e-prints, \href{https://arxiv.org/abs/2505.04698}{arXiv:2505.04698}.

96. Liu, M., Zhang, Y., Wang, Y., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Detection of an Orphan X-Ray Flare from a Blazar Candidate EP240709a with the Einstein Probe}. \apj, 984, 5. \href{https://arxiv.org/abs/2412.18463}{arXiv:2412.18463}.

95. Shrestha, M., DeSoto, S., Sand, D. J., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Spectropolarimetry of SN 2023ixf Reveals Both Circumstellar Material and an Aspherical Helium Core}. \apjl, 982, L32. \href{https://arxiv.org/abs/2410.08199}{arXiv:2410.08199}.

94. Ravi, A. P., Valenti, S., Dong, Y., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Luminous Type II Short-plateau SN 2023ufx: Asymmetric Explosion of a Partially Stripped Massive Progenitor}. \apj, 982, 12. \href{https://arxiv.org/abs/2411.02493}{arXiv:2411.02493}.

93. R\"oder, J., Wielgus, M., Lobanov, A. P., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{A multifrequency study of sub-parsec jets with the Event Horizon Telescope}. \aap, 695, A233. \href{https://arxiv.org/abs/2501.05518}{arXiv:2501.05518}.

92. Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{The persistent shadow of the supermassive black hole of M87: II. Model comparisons and theoretical interpretations}. \aap, 693, A265.

91. Yesmin, N., Pellegrino, C., Modjaz, M., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Spectral dataset of young type Ib supernovae and their time evolution}. \aap, 693, A307. \href{https://arxiv.org/abs/2409.04522}{arXiv:2409.04522}.

90. Onori, F., Nicholl, M., Ramsden, P., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{The case of AT2022wtn: a tidal disruption event in an interacting galaxy}. \mnras, 540, 498-520. \href{https://arxiv.org/abs/2504.21686}{arXiv:2504.21686}.

89. Ma, X., Wang, X., Mo, J., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Supernovae at distances <40 Mpc: II. Supernova rate in the local Universe}. \aap, 698, A306. \href{https://arxiv.org/abs/2504.04507}{arXiv:2504.04507}.

88. Ma, X., Wang, X., Mo, J., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Supernovae at distances <40 Mpc: I. Catalogues and fractions of supernovae in a complete sample}. \aap, 698, A305. \href{https://arxiv.org/abs/2504.04393}{arXiv:2504.04393}.

87. Zeng, X., Luo, Y., Wang, X., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{SN 2023xqm: A gradually fading Ia supernova exhibiting isolated high-velocity signatures}. \aap, 698, A70.

86. Zeng, X., Hu, L., Zheng, S., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{SN 2023ehl: A Normal Type Ia Supernova with High-velocity Features}. \apj, 986, 68.

85. Hsu, B., Smith, N., Goldberg, J. A., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{One Year of SN 2023ixf: Breaking through the Degenerate Parameter Space in Light-curve Models with Pulsating Progenitors}. \apj, 990, 148. \href{https://arxiv.org/abs/2408.07874}{arXiv:2408.07874}.

84. Palit, B., \'Sniegowska, M., Markowitz, A., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Markarian 590: the AGN awakens}. \mnras, 540, L14-L20. \href{https://arxiv.org/abs/2501.07225}{arXiv:2501.07225}.

83. Subrayan, B. M., Sand, D. J., Bostroem, K. A., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Early Shock Cooling Observations and Progenitor Constraints of Type IIb Supernova SN 2024uwq}. \apjl, 990, L68. \href{https://arxiv.org/abs/2505.02908}{arXiv:2505.02908}.

82. Shu, X., Yang, L., Yang, H., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{EP241021a: A Months-duration X-Ray Transient with Luminous Optical and Radio Emission}. \apjl, 990, L29. \href{https://arxiv.org/abs/2505.07665}{arXiv:2505.07665}.

81. Andrews, J. E., Shrestha, M., Bostroem, K. A., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{Asymmetries and Circumstellar Interaction in the Type II SN 2024bch}. \apj, 980, 37. \href{https://arxiv.org/abs/2411.02497}{arXiv:2411.02497}.

80. Li, W. X., Zhu, Z. P., Zou, X. Z., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{An extremely soft and weak fast X-ray transient associated with a luminous supernova}. arXiv e-prints, \href{https://arxiv.org/abs/2504.17034}{arXiv:2504.17034}.

79. Pastorello, A., Reguitti, A., Tartaglia, L., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{A long-lasting eruption heralds SN 2023ldh, a clone of SN 2009ip}. \aap, 701, A32. \href{https://arxiv.org/abs/2503.23123}{arXiv:2503.23123}.

78. Baer-Way, R., Chandra, P., Modjaz, M., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{A Multiwavelength Autopsy of the Interacting Type IIn Supernova 2020ywx: Tracing Its Progenitor Mass-loss History for 100 Yr Before Death}. \apj, 983, 101. \href{https://arxiv.org/abs/2412.06914}{arXiv:2412.06914}.

77. Kumar, H., Berger, E., Blanchard, P. K., ..., \textbf{J. R. Farah}, \textit{et al.}. 2025. \textit{A Detection of Helium in the Bright Superluminous Supernova SN 2024rmj}. arXiv e-prints, \href{https://arxiv.org/abs/2506.06417}{arXiv:2506.06417}.

76. Baczko, A. K., Kadler, M., Ros, E., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{The putative center in NGC 1052}. \aap, 692, A205. \href{https://arxiv.org/abs/2501.08685}{arXiv:2501.08685}.

75. Pellegrino, C., Modjaz, M., Takei, Y., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{The X-Ray Luminous Type Ibn SN 2022ablq: Estimates of Preexplosion Mass Loss and Constraints on Precursor Emission}. \apj, 977, 2. \href{https://arxiv.org/abs/2407.18291}{arXiv:2407.18291}.

74. Dong, Y., Tsuna, D., Valenti, S., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{SN2023fyq: A Type Ibn Supernova with Long-standing Precursor Activity Due to Binary Interaction}. \apj, 977, 254. \href{https://arxiv.org/abs/2405.04583}{arXiv:2405.04583}.

73. Newsome, M., Arcavi, I., Howell, D. A., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{Mapping the Inner 0.1 pc of a Supermassive Black Hole Environment with the Tidal Disruption Event and Extreme Coronal-line Emitter AT 2022upj}. \apj, 977, 258. \href{https://arxiv.org/abs/2406.11972}{arXiv:2406.11972}.

72. Algaba, J., Balokovi\'c, M., Chandra, S., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{Broadband multi-wavelength properties of M87 during the 2018 EHT campaign including a very high energy flaring episode}. \aap, 692, A140. \href{https://arxiv.org/abs/2404.17623}{arXiv:2404.17623}.

71. Szalai, T., K\"onyves-T\'oth, R., Nagy, A., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{The story of SN 2021aatd: A peculiar 1987A-like supernova with an early-phase luminosity excess}. \aap, 690, A17. \href{https://arxiv.org/abs/2406.02498}{arXiv:2406.02498}.

70. Dong, Y., Valenti, S., Ashall, C., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{Characterizing the Rapid Hydrogen Disappearance in SN 2022crv: Evidence of a Continuum between Type Ib and IIb Supernova Properties}. \apj, 974, 316. \href{https://arxiv.org/abs/2309.09433}{arXiv:2309.09433}.

69. Kumar, H., Berger, E., Hiramatsu, D., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{AT2023vto: An Exceptionally Luminous Helium Tidal Disruption Event from a Massive Star}. \apjl, 974, L36. \href{https://arxiv.org/abs/2408.01482}{arXiv:2408.01482}.

68. Johnson, M. D., Akiyama, K., Baturin, R., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{The Black Hole Explorer: motivation and vision}. 13092, 130922D. \href{https://arxiv.org/abs/2406.12917}{arXiv:2406.12917}.

67. Jacobson-Gal\'an, W., Dessart, L., Davis, K., \textit{et al.}. 2024. \textit{Final Moments. II. Observational Properties and Physical Modeling of Circumstellar-material-interacting Type II Supernovae}. \apj, 970, 189. \href{https://arxiv.org/abs/2403.02382}{arXiv:2403.02382}.

66. Park, S., Rho, J., Yoon, S. C., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{Optical and Infrared Observation of a Type IIP Supernova 2021qqu}. 536, 165.

65. Faris, S., Arcavi, I., Makrygianni, L., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{Light-curve Structure and H{\ensuremath{alpha}} Line Formation in the Tidal Disruption Event AT 2019azh}. \apj, 969, 104. \href{https://arxiv.org/abs/2312.03842}{arXiv:2312.03842}.

64. Kwok, L. A., Siebert, M. R., Johansson, J., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{Ground-based and JWST Observations of SN 2022pul. II. Evidence from Nebular Spectroscopy for a Violent Merger in a Peculiar Type Ia Supernova}. \apj, 966, 135. \href{https://arxiv.org/abs/2308.12450}{arXiv:2308.12450}.

63. Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{The persistent shadow of the supermassive black hole of M 87. I. Observations, calibration, imaging, and analysis}. \aap, 681, A79.

62. Pearson, J., Sand, D. J., Lundqvist, P., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{Strong Carbon Features and a Red Early Color in the Underluminous Type Ia SN 2022xkq}. \apj, 960, 29. \href{https://arxiv.org/abs/2309.10054}{arXiv:2309.10054}.

61. Siebert, M. R., Kwok, L. A., Johansson, J., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{Ground-based and JWST Observations of SN 2022pul. I. Unusual Signatures of Carbon, Oxygen, and Circumstellar Interaction in a Peculiar Type Ia Supernova}. \apj, 960, 88. \href{https://arxiv.org/abs/2308.12449}{arXiv:2308.12449}.

60. Yadavalli, S. K., Villar, V. A., Izzo, L., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{SN 2022oqm: A Bright and Multipeaked Calcium-rich Transient}. \apj, 972, 194. \href{https://arxiv.org/abs/2308.12991}{arXiv:2308.12991}.

59. Andrews, J. E., Pearson, J., Hosseinzadeh, G., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{SN 2022jox: An Extraordinarily Ordinary Type II SN with Flash Spectroscopy}. \apj, 965, 85. \href{https://arxiv.org/abs/2310.16092}{arXiv:2310.16092}.

58. Padilla Gonzalez, E., Howell, D., Terreran, G., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{SN 2022joj: A Potential Double Detonation with a Thin Helium Shell}. \apj, 964, 196. \href{https://arxiv.org/abs/2308.06334}{arXiv:2308.06334}.

57. Newsome, M., Arcavi, I., Howell, D. A., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{Probing the Subparsec Dust of a Supermassive Black Hole with the Tidal Disruption Event AT 2020mot}. \apj, 961, 239. \href{https://arxiv.org/abs/2305.03767}{arXiv:2305.03767}.

56. Paraschos, G., Kim, J. Y., Wielgus, M., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{Ordered magnetic fields around the 3C 84 central black hole}. \aap, 682, L3. \href{https://arxiv.org/abs/2402.00927}{arXiv:2402.00927}.

55. Hiramatsu, D., Matsumoto, T., Berger, E., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{Multiple Peaks and a Long Precursor in the Type IIn Supernova 2021qqp: An Energetic Explosion in a Complex Circumstellar Environment}. \apj, 964, 181. \href{https://arxiv.org/abs/2305.11168}{arXiv:2305.11168}.

54. Raymond, A. W., Doeleman, S. S., Asada, K., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{First Very Long Baseline Interferometry Detections at 870 {\ensuremath{mu}}m}. \aj, 168, 130. \href{https://arxiv.org/abs/2410.07453}{arXiv:2410.07453}.

53. Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{First Sagittarius A* Event Horizon Telescope Results. VIII. Physical Interpretation of the Polarized Ring}. \apjl, 964, L26.

52. Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{First Sagittarius A* Event Horizon Telescope Results. VII. Polarization of the Ring}. \apjl, 964, L25.

51. Shrestha, M., Bostroem, K. A., Sand, D. J., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{Extended Shock Breakout and Early Circumstellar Interaction in SN 2024ggi}. \apjl, 972, L15. \href{https://arxiv.org/abs/2405.18490}{arXiv:2405.18490}.

50. Shrestha, M., Pearson, J., Wyatt, S., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{Evidence of Weak Circumstellar Medium Interaction in the Type II SN 2023axu}. \apj, 961, 247. \href{https://arxiv.org/abs/2310.00162}{arXiv:2310.00162}.

49. Bora, Z., K\"onyves-T\'oth, R., Vink\'o, J., ..., \textbf{J. R. Farah}, \textit{et al.}. 2024. \textit{Ejecta Masses in Type Ia Supernovae---Implications for the Progenitor and the Explosion Scenario}. \pasp, 136, 094201. \href{https://arxiv.org/abs/2408.11928}{arXiv:2408.11928}.

48. Torne, P., Liu, K., Eatough, R. P., ..., \textbf{J. R. Farah}, \textit{et al.}. 2023. \textit{A Search for Pulsars around Sgr A* in the First Event Horizon Telescope Data Set}. \apj, 959, 14. \href{https://arxiv.org/abs/2308.15381}{arXiv:2308.15381}.

47. Bostroem, K. A., Pearson, J., Shrestha, M., ..., \textbf{J. R. Farah}, \textit{et al.}. 2023. \textit{Early Spectroscopy and Dense Circumstellar Medium Interaction in SN 2023ixf}. \apjl, 956, L5. \href{https://arxiv.org/abs/2306.10119}{arXiv:2306.10119}.

46. Hosseinzadeh, G., Sand, D. J., Sarbadhicary, S. K., ..., \textbf{J. R. Farah}, \textit{et al.}. 2023. \textit{The Early Light Curve of SN 2023bee: Constraining Type Ia Supernova Progenitors the Apian Way}. \apjl, 953, L15. \href{https://arxiv.org/abs/2305.03071}{arXiv:2305.03071}.

\begin{mdframed}[linecolor=red]
45. Hosseinzadeh, G., \textbf{J. R. Farah}, Shrestha, M., \textit{et al.}. 2023. \textit{Shock Cooling and Possible Precursor Emission in the Early Light Curve of the Type II SN 2023ixf}. \apjl, 953, L16. \href{https://arxiv.org/abs/2306.06097}{arXiv:2306.06097}.
\end{mdframed}

44. Bostroem, K. A., Dessart, L., Hillier, D. J., ..., \textbf{J. R. Farah}, \textit{et al.}. 2023. \textit{SN 2022acko: The First Early Far-ultraviolet Spectra of a Type IIP Supernova}. \apjl, 953, L18. \href{https://arxiv.org/abs/2305.01654}{arXiv:2305.01654}.

43. Ben-Ami, T., Arcavi, I., Newsome, M., ..., \textbf{J. R. Farah}, \textit{et al.}. 2023. \textit{The Type Ibn Supernova 2019kbj: Indications for Diversity in Type Ibn Supernova Progenitors}. \apj, 946, 30. \href{https://arxiv.org/abs/2212.03407}{arXiv:2212.03407}.

42. Shrestha, M., Sand, D. J., Alexander, K. D., ..., \textbf{J. R. Farah}, \textit{et al.}. 2023. \textit{Limit on Supernova Emission in the Brightest Gamma-Ray Burst, GRB 221009A}. \apjl, 946, L25. \href{https://arxiv.org/abs/2302.03829}{arXiv:2302.03829}.

41. Jorstad, S., Wielgus, M., Lico, R., ..., \textbf{J. R. Farah}, \textit{et al.}. 2023. \textit{The Event Horizon Telescope Image of the Quasar NRAO 530}. \apj, 943, 170. \href{https://arxiv.org/abs/2302.04622}{arXiv:2302.04622}.

40. Roelofs, F., Johnson, M. D., Chael, A., ..., \textbf{J. R. Farah}, \textit{et al.}. 2023. \textit{Polarimetric Geometric Modeling for mm-VLBI Observations of Black Holes}. \apjl, 957, L21. \href{https://arxiv.org/abs/2311.10695}{arXiv:2311.10695}.

39. Hiramatsu, D., Tsuna, D., Berger, E., ..., \textbf{J. R. Farah}, \textit{et al.}. 2023. \textit{From Discovery to the First Month of the Type II Supernova 2023ixf: High and Variable Mass Loss in the Final Year before Explosion}. \apjl, 955, L8. \href{https://arxiv.org/abs/2307.03165}{arXiv:2307.03165}.

38. Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2023. \textit{First M87 Event Horizon Telescope Results. IX. Detection of Near-horizon Circular Polarization}. \apjl, 957, L20. \href{https://arxiv.org/abs/2311.10976}{arXiv:2311.10976}.

37. Prather, B. S., Dexter, J., Moscibrodzka, M., ..., \textbf{J. R. Farah}, \textit{et al.}. 2023. \textit{Comparison of Polarized Radiative Transfer Codes Used by the EHT Collaboration}. \apj, 950, 35. \href{https://arxiv.org/abs/2303.12004}{arXiv:2303.12004}.

36. Broderick, A. E., Pesce, D. W., Gold, R., ..., \textbf{J. R. Farah}, \textit{et al.}. 2022. \textit{The Photon Ring in M87*}. \apj, 935, 61. \href{https://arxiv.org/abs/2208.09004}{arXiv:2208.09004}.

35. Issaoun, S., Wielgus, M., Jorstad, S., ..., \textbf{J. R. Farah}, \textit{et al.}. 2022. \textit{Resolving the Inner Parsec of the Blazar J1924-2914 with the Event Horizon Telescope}. \apj, 934, 145. \href{https://arxiv.org/abs/2208.01662}{arXiv:2208.01662}.

\begin{mdframed}[linecolor=red]
34.  \footnote[$^S$]{\noindent $^S$This is the first Galactic Center results series from the Event Horizon Telescope, presenting the second image of a black hole and the first horizon-scale images of Sgr A$^\ast$.}Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2022. \textit{First Sagittarius A* Event Horizon Telescope Results. VI. Testing the Black Hole Metric}. \apjl, 930, L17.

33. $^S$Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2022. \textit{First Sagittarius A* Event Horizon Telescope Results. V. Testing Astrophysical Models of the Galactic Center Black Hole}. \apjl, 930, L16.

32. $^S$Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2022. \textit{First Sagittarius A* Event Horizon Telescope Results. IV. Variability, Morphology, and Black Hole Mass}. \apjl, 930, L15. \href{https://arxiv.org/abs/2311.08697}{arXiv:2311.08697}.

31. $^S$Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2022. \textit{First Sagittarius A* Event Horizon Telescope Results. III. Imaging of the Galactic Center Supermassive Black Hole}. \apjl, 930, L14.

30. $^S$Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2022. \textit{First Sagittarius A* Event Horizon Telescope Results. II. EHT and Multiwavelength Observations, Data Processing, and Calibration}. \apjl, 930, L13.

29. $^S$Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2022. \textit{First Sagittarius A* Event Horizon Telescope Results. I. The Shadow of the Supermassive Black Hole in the Center of the Milky Way}. \apjl, 930, L12.

28. $^S$Broderick, A. E., Gold, R., Georgiev, B., ..., \textbf{J. R. Farah}, \textit{et al.}. 2022. \textit{Characterizing and Mitigating Intraday Variability: Reconstructing Source Structure in Accreting Black Holes with mm-VLBI}. \apjl, 930, L21.

27. $^S$Georgiev, B., Pesce, D. W., Broderick, A. E., ..., \textbf{J. R. Farah}, \textit{et al.}. 2022. \textit{A Universal Power-law Prescription for Variability from Synthetic Images of Black Hole Accretion Flows}. \apjl, 930, L20.
\end{mdframed}

26. Satapathy, K., Psaltis, D., \"Ozel, F., ..., \textbf{J. R. Farah}, \textit{et al.}. 2022. \textit{The Variability of the Black Hole Image in M87 at the Dynamical Timescale}. \apj, 925, 13. \href{https://arxiv.org/abs/2111.01317}{arXiv:2111.01317}.

25. Wielgus, M., Marchili, N., Mart\'\i-Vidal, I., ..., \textbf{J. R. Farah}, \textit{et al.}. 2022. \textit{Millimeter Light Curves of Sagittarius A* Observed during the 2017 Event Horizon Telescope Campaign}. \apjl, 930, L19. \href{https://arxiv.org/abs/2207.06829}{arXiv:2207.06829}.

\begin{mdframed}[linecolor=red]
24. Wielgus, M., Moscibrodzka, M., Vos, J., ..., \textbf{J. R. Farah}, \textit{et al.}. 2022. \textit{Orbital motion near Sagittarius A$^{*}$ . Constraints from polarimetric ALMA observations}. \aap, 665, L6. \href{https://arxiv.org/abs/2209.09926}{arXiv:2209.09926}.
\end{mdframed}

23. Janssen, M., Falcke, H., Kadler, M., ..., \textbf{J. R. Farah}, \textit{et al.}. 2021. \textit{Event Horizon Telescope observations of the jet launching and collimation in Centaurus A}. Nature Astronomy, 5, 1017-1028. \href{https://arxiv.org/abs/2111.03356}{arXiv:2111.03356}.

22. Narayan, R., Palumbo, D. C., Johnson, M. D., ..., \textbf{J. R. Farah}, \textit{et al.}. 2021. \textit{The Polarized Image of a Synchrotron-emitting Ring of Gas Orbiting a Black Hole}. \apj, 912, 35. \href{https://arxiv.org/abs/2105.01804}{arXiv:2105.01804}.

21. Kocherlakota, P., Rezzolla, L., Falcke, H., ..., \textbf{J. R. Farah}, \textit{et al.}. 2021. \textit{Constraints on black-hole charges with the 2017 EHT observations of M87*}. \prd, 103, 104047. \href{https://arxiv.org/abs/2105.09343}{arXiv:2105.09343}.

20. Goddi, C., Mart\'\i-Vidal, I., Messias, H., ..., \textbf{J. R. Farah}, \textit{et al.}. 2021. \textit{Polarimetric Properties of Event Horizon Telescope Targets from ALMA}. \apjl, 910, L14. \href{https://arxiv.org/abs/2105.02272}{arXiv:2105.02272}.

19. Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2021. \textit{First M87 Event Horizon Telescope Results. VIII. Magnetic Field Structure near The Event Horizon}. \apjl, 910, L13. \href{https://arxiv.org/abs/2105.01173}{arXiv:2105.01173}.

18. Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2021. \textit{First M87 Event Horizon Telescope Results. VII. Polarization of the Ring}. \apjl, 910, L12. \href{https://arxiv.org/abs/2105.01169}{arXiv:2105.01169}.

17. Raymond, A. W., Palumbo, D., Paine, S. N., ..., \textbf{J. R. Farah}, \textit{et al.}. 2021. \textit{Evaluation of New Submillimeter VLBI Sites for the Event Horizon Telescope}. \apjs, 253, 5. \href{https://arxiv.org/abs/2102.05482}{arXiv:2102.05482}.

16. Group, E. M. S. W., Algaba, J., Anczarski, J., ..., \textbf{J. R. Farah}, \textit{et al.}. 2021. \textit{Broadband Multi-wavelength Properties of M87 during the 2017 Event Horizon Telescope Campaign}. \apjl, 911, L11. \href{https://arxiv.org/abs/2104.06855}{arXiv:2104.06855}.

15. Kim, J. Y., Krichbaum, T. P., Broderick, A. E., \textit{et al.}. 2020. \textit{Event Horizon Telescope imaging of the archetypal blazar 3C 279 at an extreme 20 microarcsecond resolution}. \aap, 640, A69.

14. Johnson, M. D., Lupsasca, A., Strominger, A., ..., \textbf{J. R. Farah}, \textit{et al.}. 2020. \textit{Universal interferometric signatures of a black hole's photon ring}. Science Advances, 6, eaaz1310. \href{https://arxiv.org/abs/1907.04329}{arXiv:1907.04329}.

13. Fabbiano, G., Elvis, M., Accomazzi, A., \textit{et al.}. 2019. \textit{Increasing the Discovery Space in Astrophysics: The Exploration Question for Stars and Stellar Evolution}. \baas, 51, 85.

12. Fabbiano, G., Elvis, M., Accomazzi, A., \textit{et al.}. 2019. \textit{Increasing the Discovery Space in Astrophysics: The Exploration Question for Resolved Stellar Populations}. \baas, 51, 84.

11. Fabbiano, G., Elvis, M., Accomazzi, A., \textit{et al.}. 2019. \textit{Increasing the Discovery Space in Astrophysics: The Exploration Question for Planetary Systems}. \baas, 51, 86.

10. Fabbiano, G., Elvis, M., Accomazzi, A., \textit{et al.}. 2019. \textit{Increasing the Discovery Space in Astrophysics: The Exploration Question for Galaxy Evolution}. \baas, 51, 87.

9. Fabbiano, G., Elvis, M., Accomazzi, A., \textit{et al.}. 2019. \textit{Increasing the Discovery Space in Astrophysics: The Exploration Question for Cosmology}. \baas, 51, 88.

8. Fabbiano, G., Elvis, M., Accomazzi, A., \textit{et al.}. 2019. \textit{Increasing the Discovery Space in Astrophysics: The Exploration Question for Compact Objects}. \baas, 51, 89.

7. Fabbiano, G., Elvis, M., Accomazzi, A., \textit{et al.}. 2019. \textit{Increasing the Discovery Space in Astrophysics - A Collation of Six Submitted White Papers}. arXiv e-prints, \href{https://arxiv.org/abs/1903.06634}{arXiv:1903.06634}.

\begin{mdframed}[linecolor=red]
6. $^\dagger$Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2019. \textit{First M87 Event Horizon Telescope Results. VI. The Shadow and Mass of the Central Black Hole}. \apjl, 875, L6. \href{https://arxiv.org/abs/1906.11243}{arXiv:1906.11243}.

5. $^\dagger$Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2019. \textit{First M87 Event Horizon Telescope Results. V. Physical Origin of the Asymmetric Ring}. \apjl, 875, L5. \href{https://arxiv.org/abs/1906.11242}{arXiv:1906.11242}.

4. $^\dagger$Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2019. \textit{First M87 Event Horizon Telescope Results. IV. Imaging the Central Supermassive Black Hole}. \apjl, 875, L4. \href{https://arxiv.org/abs/1906.11241}{arXiv:1906.11241}.

3. $^\dagger$Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2019. \textit{First M87 Event Horizon Telescope Results. III. Data Processing and Calibration}. \apjl, 875, L3. \href{https://arxiv.org/abs/1906.11240}{arXiv:1906.11240}.

2. $^\dagger$Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2019. \textit{First M87 Event Horizon Telescope Results. II. Array and Instrumentation}. \apjl, 875, L2. \href{https://arxiv.org/abs/1906.11239}{arXiv:1906.11239}.

1.  \footnote[$\dagger$]{\noindent $^\dagger$These six papers are the first results papers from the Event Horizon Telescope, presenting the first image of a black hole.}Event Horizon Telescope Collaboration, ..., \textbf{J. R. Farah}, \textit{et al.}. 2019. \textit{First M87 Event Horizon Telescope Results. I. The Shadow of the Supermassive Black Hole}. \apjl, 875, L1. \href{https://arxiv.org/abs/1906.11238}{arXiv:1906.11238}.
\end{mdframed}


\vspace{+.4cm}
\section{\sc Conference publications}
(last updated: Aug 2025)

M. D. Johnson, K. Akiyama, R. Baturin, ...\textbf{J. Farah} et al. (2024). \textit{The Black Hole Explorer: motivation and vision}. In: Space Telescopes and Instrumentation 2024: Optical, Infrared, and Millimeter Wave (SPIE Conf. Ser. 13092), 130922D.

Haworth, K., Johnson, M.~D., Pesce, D.~W., ... \textbf{J. R. Farah}  et al.\ 2019. \textit{Studying black holes on horizon scales with space-VLBI}. arXiv:1909.01405 

Blackburn, L., Doeleman, S., Dexter, J., ... \textbf{J. R. Farah} et al.\ 2019. \textit{Studying Black Holes on Horizon Scales with VLBI Ground Arrays}. arXiv:1909.01411 

Fabbiano, E., Berriman, B., Bose, C., ... \textbf{J. R. Farah}, et al. 2019. \textit{Increasing the Discovery Space in Astrophysics - A Collation of Six Submitted White Papers.} 


\vspace{+.4cm}
\section{\sc Technical publications}
(last updated: Aug 2025)

Chael A., Bouman, K., Johnson  M., Wielgus M., Blackburn L., Chan C., \textbf{Farah J.}, Palumbo D., Pesce D., et al. 2022. \textit{eht-imaging: v1.2.4: Imaging interferometric data with regularized maximum likelihood}. Zenodo (software) publication.

Chael A., Bouman, K., Johnson  M., Wielgus M., Blackburn L., Chan C., \textbf{Farah J.}, Palumbo D., Pesce D. 2019. \textit{eht-imaging: v1.1.0: Imaging interferometric data with regularized maximum likelihood}. Zenodo (software) publication.

\textbf{Farah J}, Felt N, Franklin M, Giorimini P, Rogan C, Tuna A, Wang A. 2017. \textit{All The Sparks We Cannot See}. ATLAS Internal Note.

\textbf{Farah J}, Felt N, Frank, Giorimini P, Rogan C, Tuna A, Wang A. 2017. \textit{Test of the Micromegas Trigger Processor with Cosmic Ray Muons}. ATLAS Internal Note.

Felt N, Franklin M, Giorimini P, Rogan C, Tuna A, Wang A, \textbf{Farah J}. 2017. \textit{Performance of a Micromegas octuplet after removing the major cause of MMFE8 noise}. ATLAS Internal Note.

\vspace{+.4cm}
\section{\sc Classifications, telegrams, and circulars}
(last updated: Aug 2025)
%% using icarus from ADS
\bibitem[Farah et al.(2025)]{2025TNSCR3013....1F} Farah, J., Andrews, M., Wynn, K., Howell, D.~A., McCully, C.\ 2025.\ Global SN Project Transient Classification Report for 2025-07-31.\ Transient Name Server Classification Report 2025-3013.
\bibitem[Andrews et al.(2025)]{2025TNSCR2699....1A} Andrews, M., Farah, J., Wynn, K., Bosteroem, A., Howell, D.~A., McCully, C.\ 2025.\ Global SN Project Transient Classification Report for 2025-07-14.\ Transient Name Server Classification Report 2025-2699.
\bibitem[Li et al.(2025)]{2025GCN.40975....1L} Li, W.~X. and 8 colleagues 2025.\ EP250704a/GRB 250704B: GSP observations of the optical counterpart.\ GRB Coordinates Network, Circular Service, No. 40975 40975.
\bibitem[Farah et al.(2025)]{2025TNSCR2162....1F} Farah, J., Andrew, M., Howell, D.~A., McCully, C., Ni, Y.~Q., Wynn, K.\ 2025.\ Global SN Project Transient Classification Report for 2025-06-09.\ Transient Name Server Classification Report 2025-2162.
\bibitem[Ni et al.(2025)]{2025TNSCR2041....1N} Ni, C., Andrews, M., Farah, J., Wynn, K., Howell, D.~A., McCully, C.\ 2025.\ Global SN Project Transient Classification Report for 2025-05-30.\ Transient Name Server Classification Report 2025-2041.
\bibitem[Ni et al.(2025)]{2025TNSCR2027....1N} Ni, C., Andrews, M., Farah, J., Wynn, K., Howell, D.~A., McCully, C.\ 2025.\ Global SN Project Transient Classification Report for 2025-05-29.\ Transient Name Server Classification Report 2025-2027.
\bibitem[Andrews et al.(2025)]{2025TNSCR1947....1A} Andrews, M., Farah, J., Ni, C., Wynn, K., Howell, D.~A., McCully, C.\ 2025.\ Global SN Project Transient Classification Report for 2025-05-24.\ Transient Name Server Classification Report 2025-1947.
\bibitem[Ni et al.(2025)]{2025TNSCR1733....1N} Ni, C., Andrews, M., Farah, J., Wynn, K., Howell, D.~A., McCully, C.\ 2025.\ Global SN Project Transient Classification Report for 2025-05-09.\ Transient Name Server Classification Report 2025-1733.
\bibitem[Baldini et al.(2025)]{2025TNSCR1720....1B} Baldini, P. and 7 colleagues 2025.\ Transient Classification Report for 2025-05-08.\ Transient Name Server Classification Report 2025-1720.
\bibitem[Baldini et al.(2025)]{2025TNSAN.142....1B} Baldini, P. and 7 colleagues 2025.\ Spectroscopic classification of the re-brightening associated with AT 2021gqu as a SNIa-pec..\ Transient Name Server AstroNote 142.
\bibitem[Andrews et al.(2025)]{2025TNSCR1539....1A} Andrews, M., Farah, J., Ni, C., Wynn, K., Howell, D.~A., McCully, C.\ 2025.\ Global SN Project Transient Classification Report for 2025-04-25.\ Transient Name Server Classification Report 2025-1539.
\bibitem[Andrews et al.(2025)]{2025TNSCR1531....1A} Andrews, M., Farah, J., Ni, C., Wynn, K., Howell, D.~A., McCully, C.\ 2025.\ Global SN Project Transient Classification Report for 2025-04-24.\ Transient Name Server Classification Report 2025-1531.
\bibitem[Newsome et al.(2025)]{2025TNSCR1351....1N} Newsome, M. and 8 colleagues 2025.\ Transient Classification Report for 2025-04-10.\ Transient Name Server Classification Report 2025-1351.
\bibitem[Li et al.(2025)]{2025GCN.40157....1L} Li, W.~X. and 8 colleagues 2025.\ EP250416a: GSP optical upper limit.\ GRB Coordinates Network, Circular Service, No. 40157 40157.
\bibitem[Andrews et al.(2025)]{2025TNSCR1076....1A} Andrews, M., Farah, J., Howell, D.~A., McCully, C.\ 2025.\ Transient Classification Report for 2025-03-21.\ Transient Name Server Classification Report 2025-1076.
\bibitem[Andrews et al.(2025)]{2025TNSCR1033....1A} Andrews, M., Farah, J., Howell, D.~A., McCully, C.\ 2025.\ Transient Classification Report for 2025-03-18.\ Transient Name Server Classification Report 2025-1033.
\bibitem[Andrews et al.(2025)]{2025TNSCR.991....1A} Andrews, M., Farah, J., Howell, D.~A., McCully, C.\ 2025.\ Transient Classification Report for 2025-03-14.\ Transient Name Server Classification Report 2025-991.
\bibitem[Andrews et al.(2025)]{2025TNSCR.977....1A} Andrews, M., Farah, J., Howell, D.~A., McCully, C.\ 2025.\ Transient Classification Report for 2025-03-13.\ Transient Name Server Classification Report 2025-977.
\bibitem[Farah et al.(2025)]{2025TNSCR.922....1F} Farah, J., Andrews, M., Ni, C., Howell, D.~A., McCully, C.\ 2025.\ Transient Classification Report for 2025-03-08.\ Transient Name Server Classification Report 2025-922.
\bibitem[Andrews et al.(2025)]{2025TNSCR.914....1A} Andrews, M. and 6 colleagues 2025.\ Transient Classification Report for 2025-03-07.\ Transient Name Server Classification Report 2025-914.
\bibitem[Shrestha et al.(2025)]{2025GCN.39896....1S} Shrestha, M. and 13 colleagues 2025.\ GRB 250327B: Las Cumbres optical counterpart detection.\ GRB Coordinates Network, Circular Service, No. 39896 39896.
\bibitem[Li et al.(2025)]{2025GCN.39627....1L} Li, W.~X. and 8 colleagues 2025.\ EP250308a: GSP optical upper limit.\ GRB Coordinates Network, Circular Service, No. 39627 39627.
\bibitem[Andrews et al.(2025)]{2025TNSCR.802....1A} Andrews, M., Hiramatsu, D., Farah, J., Howell, D.~A., McCully, C.\ 2025.\ Transient Classification Report for 2025-02-26.\ Transient Name Server Classification Report 2025-802.
\bibitem[Farah et al.(2025)]{2025TNSCR.530....1F} Farah, J., Andrews, M., Ni, C., Howell, D.~A., McCully, C., Wynn, K.\ 2025.\ Transient Classification Report for 2025-02-07.\ Transient Name Server Classification Report 2025-530.
\bibitem[Li et al.(2025)]{2025GCN.39489....1L} Li, W.~X. and 8 colleagues 2025.\ EP250226a/GRB 250226A: GSP detects optical counterpart.\ GRB Coordinates Network, Circular Service, No. 39489 39489.
\bibitem[Li et al.(2025)]{2025GCN.39477....1L} Li, W.~X. and 8 colleagues 2025.\ EP250225a: GSP optical upper limit.\ GRB Coordinates Network, Circular Service, No. 39477 39477.
\bibitem[Faris et al.(2025)]{2025TNSCR..25....1F} Faris, S. and 6 colleagues 2025.\ StarDestroyers Transient Classification Report for 2025-01-02.\ Transient Name Server Classification Report 2025-25.
\bibitem[Andrews et al.(2024)]{2024TNSCR4593....1A} Andrews, M., Farah, J., Ni, C., Howell, D.~A., McCully, C.\ 2024.\ Global SN Project Transient Classification Report for 2024-11-22.\ Transient Name Server Classification Report 2024-4593.
\bibitem[Newsome et al.(2024)]{2024TNSCR4486....1N} Newsome, M. and 6 colleagues 2024.\ Transient Classification Report for 2024-11-13.\ Transient Name Server Classification Report 2024-4486.
\bibitem[Newsome et al.(2024)]{2024TNSCR4446....1N} Newsome, M. and 6 colleagues 2024.\ Transient Classification Report for 2024-11-11.\ Transient Name Server Classification Report 2024-4446.
\bibitem[Faris et al.(2024)]{2024TNSCR4428....1F} Faris, S. and 6 colleagues 2024.\ StarDestroyers Transient Classification Report for 2024-11-10.\ Transient Name Server Classification Report 2024-4428.
\bibitem[Newsome et al.(2024)]{2024TNSCR4337....1N} Newsome, M. and 6 colleagues 2024.\ Transient Classification Report for 2024-11-05.\ Transient Name Server Classification Report 2024-4337.
\bibitem[Li et al.(2024)]{2024GCN.38338....1L} Li, W.~X. and 8 colleagues 2024.\ EP241126a: GSP detects optical counterpart.\ GRB Coordinates Network, Circular Service, No. 38338 38338.
\bibitem[Li et al.(2024)]{2024GCN.38127....1L} Li, W.~X. and 8 colleagues 2024.\ EP241107a: GSP detects optical counterpart.\ GRB Coordinates Network, Circular Service, No. 38127 38127.
\bibitem[Faris et al.(2024)]{2024TNSCR4005....1F} Faris, S. and 6 colleagues 2024.\ StarDestroyers Transient Classification Report for 2024-10-14.\ Transient Name Server Classification Report 2024-4005.
\bibitem[Shrestha et al.(2024)]{2024GCN.37913....1S} Shrestha, M. and 11 colleagues 2024.\ GRB 241026A: Las Cumbres optical detection.\ GRB Coordinates Network, Circular Service, No. 37913 37913.
\bibitem[Li et al.(2024)]{2024GCN.37844....1L} Li, W.~X. and 8 colleagues 2024.\ EP241021a: GSP detects optical candidate counterpart.\ GRB Coordinates Network, Circular Service, No. 37844 37844.
\bibitem[Newsome et al.(2024)]{2024TNSCR3794....1N} Newsome, M., Andrews, M., Farah, J., Howell, D.~A., McCully, C.\ 2024.\ Global SN Project Transient Classification Report for 2024-09-30.\ Transient Name Server Classification Report 2024-3794.
\bibitem[Andrews et al.(2024)]{2024TNSCR3490....1A} Andrews, M., Farah, J., Howell, D.~A., McCully, C.\ 2024.\ Transient Classification Report for 2024-09-13.\ Transient Name Server Classification Report 2024-3490.

\bibitem[Andrews et al.(2024)]{2024TNSCR3471....1A} Andrews, M., Farah, J., Howell, D.~A., McCully, C.\ 2024.\ Transient Classification Report for 2024-09-12.\ Transient Name Server Classification Report 2024-3471.
\bibitem[Bostroem et al.(2024)]{2024TNSCR2571....1B} Bostroem, K.~A. and 24 colleagues 2024.\ DLT40 Transient Classification Report for 2024-07-24.\ Transient Name Server Classification Report 2024-2571.
\bibitem[Newsome et al.(2024)]{2024TNSCR1687....1N} Newsome, M., Farah, J., Howell, D.~A., McCully, C., Gonzalez, E.~P., Terreran, G.\ 2024.\ Global SN Project Transient Classification Report for 2024-05-28.\ Transient Name Server Classification Report 2024-1687.
\bibitem[Hosseinzadeh et al.(2024)]{2024TNSCR1686....1H} Hosseinzadeh, G. and 8 colleagues 2024.\ Global SN Project Transient Classification Report for 2024-05-28.\ Transient Name Server Classification Report 2024-1686.
\bibitem[Terreran et al.(2024)]{2024TNSCR.843....1T} Terreran, G., Howell, D.~A., McCully, C., Newsome, M., Gonzalez, E.~P., Farah, J.\ 2024.\ Global SN Project Transient Classification Report for 2024-03-28.\ Transient Name Server Classification Report 2024-843.
\bibitem[Terreran et al.(2024)]{2024TNSCR.828....1T} Terreran, G., Howell, D.~A., McCully, C., Newsome, M., Gonzalez, E.~P., Farah, J.\ 2024.\ Global SN Project Transient Classification Report for 2024-03-27.\ Transient Name Server Classification Report 2024-828.
\bibitem[Newsome et al.(2024)]{2024TNSCR.505....1N} Newsome, M. and 7 colleagues 2024.\ Global SN Project Transient Classification Report for 2024-02-21.\ Transient Name Server Classification Report 2024-505.
\bibitem[Newsome et al.(2024)]{2024TNSCR.448....1N} Newsome, M., Farah, J., Howell, D.~A., McCully, C., Gonzalez, E.~P., Terreran, G.\ 2024.\ Global SN Project Transient Classification Report for 2024-02-14.\ Transient Name Server Classification Report 2024-448.
\bibitem[Newsome et al.(2024)]{2024TNSCR.413....1N} Newsome, M., Farah, J., Howell, D.~A., McCully, C., Gonzalez, E.~P., Terreran, G.\ 2024.\ Global SN Project Transient Classification Report for 2024-02-12.\ Transient Name Server Classification Report 2024-413.
\bibitem[Gonzalez et al.(2024)]{2024TNSCR.399....1G} Gonzalez, E.~P. and 6 colleagues 2024.\ Global SN Project Transient Classification Report for 2024-02-11.\ Transient Name Server Classification Report 2024-399.
\bibitem[Newsome et al.(2024)]{2024TNSCR.344....1N} Newsome, M. and 8 colleagues 2024.\ Global SN Project Transient Classification Report for 2024-02-04.\ Transient Name Server Classification Report 2024-344.
\bibitem[Newsome et al.(2024)]{2024TNSCR.261....1N} Newsome, M. and 6 colleagues 2024.\ Global SN Project Transient Classification Report for 2024-01-26.\ Transient Name Server Classification Report 2024-261.
\bibitem[Terreran et al.(2024)]{2024TNSCR.232....1T} Terreran, G. and 6 colleagues 2024.\ Global SN Project Transient Classification Report for 2024-01-22.\ Transient Name Server Classification Report 2024-232.
\bibitem[Newsome et al.(2024)]{2024TNSCR..44....1N} Newsome, M. and 6 colleagues 2024.\ Global SN Project Transient Classification Report for 2024-01-05.\ Transient Name Server Classification Report 2024-44.
\bibitem[Arcavi et al.(2023)]{2023TNSCR3391....1A} Arcavi, I., Terreran, G., Newsome, M., Farah, J., Charalampopoulos, P.\ 2023.\ StarDestroyers Transient Classification Report for 2023-12-30.\ Transient Name Server Classification Report 2023-3391.
\bibitem[Terreran et al.(2023)]{2023TNSCR3376....1T} Terreran, G., Howell, D.~A., McCully, C., Newsome, M., Gonzalez, E.~P., Farah, J.\ 2023.\ Global SN Project Transient Classification Report for 2023-12-28.\ Transient Name Server Classification Report 2023-3376.
\bibitem[Farah et al.(2023)]{2023TNSCR2992....1F} Farah, J. and 6 colleagues 2023.\ Transient Classification Report for 2023-11-17.\ Transient Name Server Classification Report 2023-2992.
\bibitem[Newsome et al.(2023)]{2023TNSCR2557....1N} Newsome, M., Farah, J., Howell, D.~A., McCully, C., Gonzalez, E.~P., Terreran, G.\ 2023.\ Global SN Project Transient Classification Report for 2023-10-11.\ Transient Name Server Classification Report 2023-2557.
\bibitem[Gonzalez et al.(2023)]{2023TNSCR2348....1G} Gonzalez, E.~P. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-09-21.\ Transient Name Server Classification Report 2023-2348.
\bibitem[Pellegrino et al.(2023)]{2023TNSCR2244....1P} Pellegrino, C. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-09-12.\ Transient Name Server Classification Report 2023-2244.
\bibitem[Farah et al.(2023)]{2023TNSCR2213....1F} Farah, J. and 6 colleagues 2023.\ Transient Classification Report for 2023-09-08.\ Transient Name Server Classification Report 2023-2213.
\bibitem[Terreran et al.(2023)]{2023TNSCR2212....1T} Terreran, G. and 6 colleagues 2023.\ Transient Classification Report for 2023-09-08.\ Transient Name Server Classification Report 2023-2212.
\bibitem[Terreran et al.(2023)]{2023TNSCR2162....1T} Terreran, G. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-09-04.\ Transient Name Server Classification Report 2023-2162.
\bibitem[Pellegrino et al.(2023)]{2023TNSCR2134....1P} Pellegrino, C. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-08-31.\ Transient Name Server Classification Report 2023-2134.
\bibitem[Gonzalez et al.(2023)]{2023TNSCR2054....1G} Gonzalez, E.~P. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-08-23.\ Transient Name Server Classification Report 2023-2054.
\bibitem[Newsome et al.(2023)]{2023TNSCR2033....1N} Newsome, M. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-08-21.\ Transient Name Server Classification Report 2023-2033.
\bibitem[Newsome et al.(2023)]{2023TNSCR1999....1N} Newsome, M. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-08-17.\ Transient Name Server Classification Report 2023-1999.
\bibitem[Farah et al.(2023)]{2023TNSCR1960....1F} Farah, J. and 6 colleagues 2023.\ Transient Classification Report for 2023-08-14.\ Transient Name Server Classification Report 2023-1960.
\bibitem[Newsome et al.(2023)]{2023TNSCR1865....1N} Newsome, M. and 8 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-08-05.\ Transient Name Server Classification Report 2023-1865.
\bibitem[Newsome et al.(2023)]{2023TNSCR1767....1N} Newsome, M. and 7 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-07-25.\ Transient Name Server Classification Report 2023-1767.
\bibitem[Newsome et al.(2023)]{2023TNSCR1754....1N} Newsome, M. and 8 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-07-24.\ Transient Name Server Classification Report 2023-1754.
\bibitem[Gonzalez et al.(2023)]{2023TNSCR1753....1G} Gonzalez, E.~P. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-07-24.\ Transient Name Server Classification Report 2023-1753.
\bibitem[Newsome et al.(2023)]{2023TNSCR1737....1N} Newsome, M. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-07-22.\ Transient Name Server Classification Report 2023-1737.
\bibitem[Gonzalez et al.(2023)]{2023TNSCR1496....1G} Gonzalez, E.~P. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-06-26.\ Transient Name Server Classification Report 2023-1496.
\bibitem[Pellegrino et al.(2023)]{2023TNSCR1474....1P} Pellegrino, C. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-06-23.\ Transient Name Server Classification Report 2023-1474.
\bibitem[Pellegrino et al.(2023)]{2023TNSCR1279....1P} Pellegrino, C. and 7 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-05-30.\ Transient Name Server Classification Report 2023-1279.
\bibitem[Farah et al.(2023)]{2023TNSCR1137....1F} Farah, J. and 6 colleagues 2023.\ Transient Classification Report for 2023-05-17.\ Transient Name Server Classification Report 2023-1137.
\bibitem[Gonzalez et al.(2023)]{2023TNSCR1017....1G} Gonzalez, E.~P. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-05-05.\ Transient Name Server Classification Report 2023-1017.
\bibitem[Newsome et al.(2023)]{2023TNSCR.944....1N} Newsome, M. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-04-27.\ Transient Name Server Classification Report 2023-944.
\bibitem[Farah et al.(2023)]{2023TNSCR.793....1F} Farah, J. and 6 colleagues 2023.\ Transient Classification Report for 2023-04-14.\ Transient Name Server Classification Report 2023-793.
\bibitem[Pellegrino et al.(2023)]{2023TNSCR.725....1P} Pellegrino, C. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-04-06.\ Transient Name Server Classification Report 2023-725.
\bibitem[Pellegrino et al.(2023)]{2023TNSAN..75....1P} Pellegrino, C. and 6 colleagues 2023.\ Classification of AT 2023emq as a Type Icn Supernova.\ Transient Name Server AstroNote 75.
\bibitem[Pellegrino et al.(2023)]{2023TNSCR.542....1P} Pellegrino, C. and 7 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-03-15.\ Transient Name Server Classification Report 2023-542.
\bibitem[Terreran et al.(2023)]{2023TNSCR.490....1T} Terreran, G. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-03-07.\ Transient Name Server Classification Report 2023-490.
\bibitem[Hosseinzadeh et al.(2023)]{2023TNSCR.277....1H} Hosseinzadeh, G. and 8 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-02-03.\ Transient Name Server Classification Report 2023-277.
\bibitem[Pellegrino et al.(2023)]{2023TNSCR.218....1P} Pellegrino, C. and 6 colleagues 2023.\ Global SN Project Transient Classification Report for 2023-01-27.\ Transient Name Server Classification Report 2023-218.
\bibitem[Farah et al.(2023)]{2023TNSCR.144....1F} Farah, J. and 6 colleagues 2023.\ Transient Classification Report for 2023-01-20.\ Transient Name Server Classification Report 2023-144.
\bibitem[Pellegrino et al.(2022)]{2022TNSCR2757....1P} Pellegrino, C. and 8 colleagues 2022.\ Global SN Project Transient Classification Report for 2022-09-23.\ Transient Name Server Classification Report 2022-2757.
\bibitem[Pellegrino et al.(2022)]{2022TNSCR2707....1P} Pellegrino, C. and 7 colleagues 2022.\ Global SN Project Transient Classification Report for 2022-09-19.\ Transient Name Server Classification Report 2022-2707.
\bibitem[Pellegrino et al.(2022)]{2022TNSCR2535....1P} Pellegrino, C. and 8 colleagues 2022.\ Global SN Project Transient Classification Report for 2022-08-31.\ Transient Name Server Classification Report 2022-2535.
\bibitem[Pellegrino et al.(2022)]{2022TNSCR2510....1P} Pellegrino, C. and 7 colleagues 2022.\ Global SN Project Transient Classification Report for 2022-08-29.\ Transient Name Server Classification Report 2022-2510.

% \section{\sc Journal Publications}
% \vspace{+.4cm}
% \section{\sc Invited Talks}
% \vspace{+.4cm}
% \section{\sc Teaching}
% \vspace{+.4cm}

\end{resume}

\end{document}




